---
title: "linear model from Web"
author: "Paulo Poblete"
date: "Fall 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```


The scatter plot above looks like a bunch of them are moving upwards to the right. My suspicion is a postie correlation since its going uphill to the right. 

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation we found is 0.69, which is a positive correlation. 

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation of a line is y = mx + b  
The fit equation is SIMS = 0.054563*ARM -4.095160  

#### Predict at target point

SIMS = 0.054563*88 -4.095160  

```{r}
0.054563*88-4.095160  
```

When we plugged in 88 for the arm we got 0.706384. This is my prediction on the value.

```{r}
new  <- data.frame(ARM = 88,GRIP = 94)
```
```{r}
predict(model.1,new,interval = "prediction")
```

Using the predict function gives us as the same result
0.706403

#### scatterplot with model fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point()
basicNN + geom_point() + geom_smooth(method=lm)
```


Here is the best fit line for the data, and we can clearly see that if we look for an x value of 88 for the arm and the value of y is 0.7 as predicted. 

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

The scatterplot shows that its a positive correlation since its going upwards to the right. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

GRIP has a smaller correlation than with SIMS with GRIP VS SIMS with ARM  
  

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

If we look at the R-Squared value of this GRIP data, its smaller that the ARMS data adjusted R-Squared. Furthermore, the residual standard error is larger for the GRIP Data rather than the ARM data. Both of them indicate that Model 1 is doing a way better job at explaining our prediction, and a better model.  


#### predict model.2 at target point

```{r}
predict(model.2,new,interval = "predict")
```
```{r}
0.045463*94-4.809675
```



#### now add the model fit to our plot for model.2

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
basicNN + geom_point() + geom_smooth(method=lm)
```

Up above is the results of the scatter plot and the best FIT line for our SIMS and GRIP data. If we use our prediction value mathes x=94 for GRIP. 



## Model 3 SIM~ARM+GRIP

### Numerical results (cor)
```{r}
cor(SIMS~ARM+GRIP,data=data)
```
We have a positive corrleation between both ARM and GRIP data. The number is higher than the correlation of just ARM and SIMS or GRIP and SIMS. 


### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~GRIP + ARM,data=data)
summary.lm(model.3)
```

SIMS = -5.43 + GRIP * 0.02 + ARM * 0.04  
Our residual standard error is 1.144  which is smaller than our other models, and our multiple R - Sq  is bigger, which makes it a better fit model. 


#### predict model.3 at target point
```{r}
predict(model.3,new,interval = "predict")
```



## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

